Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-18 bbbq_article.tex
Remove wooly part, thanks Geert

We grouped all epitopes presented by MHC-I and MHC-II alleles and show 
the percentage of which these were TMH-derived in figure \ref{fig:2b},
which are 22\% and 10\%. \textbf{GEERT: zou je ook geen horizontale rode streep kunnen trekken op de verwachtingswaardes, net al in Fig 1A? Dan zie je dat het hoger is}

\textbf{GEERT: zie voorgaande punt aangaande verwachtingwaarde. De gevonden waardes zijn hoger, dus zoek je in volgende stuk tekst naar problemen die er niet zijn, en zou dit dus weg laten. Is onduidelijk en wollig stuk: The percentage of TMH derived epitopes is relatively high
for both sources of epitopes, which are (1) the predicted 
9-mers (for MHC-I) and 14-mers (for MHC-II) from
a reference human proteome  (see Figure \ref{fig:bbbq_1_smart_results}),
(2) the IEBD epitopes from MHC ligand assays (Figure \ref{fig:2a}).
These results cannot be compared with an \emph{a priori}
expactation, as the predicted percentages are biased by
(I) the expression of the probed proteins and cleavage sites, 
(II) the bias in mass spectrometry towards hydrophillic peptides 
and (III) availablilty of data for the different alleles.
}

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles
    that overlap with TMHs that are presented.
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval. Note that only one line is visible as this
    interval is relatively narrow.
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. 
  }
  \label{fig:elution}
\end{figure}

>>>>

We grouped all epitopes presented by MHC-I and MHC-II alleles and show 
the percentage of which these were TMH-derived in figure \ref{fig:2b},
which are 22\% and 10\%.

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles
    that overlap with TMHs that are presented.
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval. Note that only one line is visible as this
    interval is relatively narrow.
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. 
  }
  \label{fig:elution}
\end{figure}
